On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-31 docs/mvfits_paper/mvf.tex
Up to describe w220 comp with Nagar et al. [15]

  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. (Bottom) Percentage absolute residual errors for fits of dimensionless \qnm{} frequencies,, $\cw\lmn$ along with select numerical values (colored markers) computed using Leaver's method \cite{Leaver85}. For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray. }

@@

here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves.

@@

\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.

>>>>

  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. (Bottom) Percentage absolute residual errors for fits of dimensionless \qnm{} frequencies,, $\cw\lmn$ along with select numerical values (colored markers) computed using Leaver's method \cite{Leaver85}. For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray and a single residual using a fit for $\cw_{220}$ from \cite{Nagar:2018zoe} is shown as an orange dashed line.}

@@

here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves. A residual error is also shown as an orange dashed line for the $\cw_{220}$ model presented in Ref.~\cite{Nagar:2018zoe}. This is a rational model with 14 fitted parameters compared to the polynomial model with 10 fitted parameters defined in \eqn{eq:cw_fit_1}. We observe that Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$.

@@

\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting polynomial models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature. We note our comparison of $\cw_{220}$ from Ref.~\cite{Nagar:2018zoe} suggests even better fits for $(l,m,n)\neq(2,2,0)$ QNM frequencies might be achievable using a rational ansatz. We leave this extension to future modeling work.
